Moral Foundations of U.S. Political News Organizations

### 2018-12-04 pilot_manuscript.Rmd
i don't know what i did

This issue is compounded by the fact the Moral Foundations Questionnaire (MFQ) and its subscales assume endorsement lies on a continuum. One item under the *fairness/reciprocity* judgment subscale reads, "Justice is the most important requirement for a society" [@GILLIGAN1991]. The survey respondent must select a number on a scale from 1 to 6 indicating responses spanning "strongly disagree" at 1 to "strongly agree" at 6. While the scales in the MFQ do not represent true valence as it pertains to individual words, it does allow for a greater degree of specificity in terms of an individual's endorsement of a particular moral foundation. When a respondent selects a 4 for the aforementioned MFQ statement, they clearly are indicating they "slightly agree" with the statement [@GILLIGAN1991]. This specificity is not present in most analyses involving the MFD and percent occurence, unless they also take into account the valence of the words used in the text or speech of interest.

@@

The source article words were compiled into a dataset where they were matched up with their counterparts in the MFD along with their valence and a percentage of their occurrence. Therefore, for each article, the percentage of the number of *harm/care* words occurring in the articles were calculated, and this process was repeated for each of the foundations. This procedure created five percentages that were included as the dependent variable for the following analyses. 
```{r stem_text, eval=TRUE, include=FALSE}

@@

tableprint[ , c(2:6, 8)] = printnum(as.numeric(tableprint[ , c(2:6, 8)]))
tableprint[ , 7] = printp(as.numeric(tableprint[ , 7]))
```
# Discussion

>>>>

This issue is compounded by the fact the Moral Foundations Questionnaire (MFQ) and its subscales assume endorsement lies on a continuum. One item under the *fairness/reciprocity* judgment subscale reads, "Justice is the most important requirement for a society" [@Graham2011]. The survey respondent must select a number on a scale from 1 to 6 indicating responses spanning "strongly disagree" at 1 to "strongly agree" at 6. While the scales in the MFQ do not represent true valence as it pertains to individual words, it does allow for a greater degree of specificity in terms of an individual's endorsement of a particular moral foundation. When a respondent selects a 4 for the aforementioned MFQ statement, they clearly are indicating they "slightly agree" with the statement [@Graham2011]. This specificity is not present in most analyses involving the MFD and percent occurence, unless they also take into account the valence of the words used in the text or speech of interest.

@@

The source article words were compiled into a dataset where they were matched up with their counterparts in the MFD along with their valence and a percentage of their occurrence. Therefore, for each article, the percentage of the number of *harm/care* words occurring in the articles were calculated, and this process was repeated for each of the foundations. This procedure created five percentages that were included as the dependent variable for the following analyses.

```{r stem_text, eval=TRUE, include=FALSE}

@@

tableprint[ , c(2:6, 8)] = printnum(as.numeric(tableprint[ , c(2:6, 8)]))
tableprint[ , 7] = printp(as.numeric(tableprint[ , 7]))

apa_table(tableprint,
          note = "something useful here",
          caption = "stuff at the top", 
          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
          format = "latex",
          escape = F,
          align = c("l", rep("c", 7))
          )
```
# Discussion

### 2018-12-04 pilot_manuscript.tex
i don't know what i did

\#\#Moral Foundations Theory

@@

The researchers settled on these specific foundations after the
completion of a literature survey of research in anthropology and
evolutionary psychology ({\textbf{???}}). \emph{LET'S CHECK THIS
CITATION IN MENDELEY}!.The first two foundations (\emph{harm/care} and
\emph{fairness/reciprocity}) are termed the \enquote{individualizing
foundations,} as they are centered on the concerns of individuals rather
than groups. \emph{Harm/care} represents an endorsement of compassion
and kindness, while opposing cruelty and harm.
\emph{Fairness/reciprocity} represents concerns centered on guaranteeing
individual rights as well as justice and equality among all people. The
other three foundations (\emph{ingroup/loyalty},
\emph{authority/respct}, and \emph{purity/sanctity}) are the
\enquote{binding} foundations, owing to their focus on group-related
concerns, rather than those of individuals. \emph{Ingroup/loyalty}
represents endorsements of patriotism and heroism and discourages
nonconformity and dissent. \emph{Authority/respect} represents an
endorsement of social hierarchies and traditions while denigrating
disobedience. Finally, \emph{purity/sanctity} represents concerns
regarding chastity and piety, while discouraging vices and indulgences,
including lust, avarice, and gluttony ({\textbf{???}}). Liberals tend to
endorse the individualizing foundations more than conservatives.
Endorsements for the three binding foundations, however, are lower than
conservatives. Conservatives, on the other hand, tend to endorse all
five foundations equally, implying they base judments (at least
partially) on each foundation ({\textbf{???}}).

\#\#Moral Foundations Dictionary

@@

\#\#Valence

@@

@@

\#\#Kavanaugh Supreme Court Hearing

>>>>

\hypertarget{moral-foundations-theory}{%
\subsection{Moral Foundations Theory}\label{moral-foundations-theory}}

@@

The researchers settled on these specific foundations after the
completion of a literature survey of research in anthropology and
evolutionary psychology ({\textbf{???}}).The first two foundations
(\emph{harm/care} and \emph{fairness/reciprocity}) are termed the
\enquote{individualizing foundations,} as they are centered on the
concerns of individuals rather than groups. \emph{Harm/care} represents
an endorsement of compassion and kindness, while opposing cruelty and
harm. \emph{Fairness/reciprocity} represents concerns centered on
guaranteeing individual rights as well as justice and equality among all
people. The other three foundations (\emph{ingroup/loyalty},
\emph{authority/respct}, and \emph{purity/sanctity}) are the
\enquote{binding} foundations, owing to their focus on group-related
concerns, rather than those of individuals. \emph{Ingroup/loyalty}
represents endorsements of patriotism and heroism and discourages
nonconformity and dissent. \emph{Authority/respect} represents an
endorsement of social hierarchies and traditions while denigrating
disobedience. Finally, \emph{purity/sanctity} represents concerns
regarding chastity and piety, while discouraging vices and indulgences,
including lust, avarice, and gluttony ({\textbf{???}}). Liberals tend to
endorse the individualizing foundations more than conservatives.
Endorsements for the three binding foundations, however, are lower than
conservatives. Conservatives, on the other hand, tend to endorse all
five foundations equally, implying they base judments (at least
partially) on each foundation ({\textbf{???}}).

\hypertarget{moral-foundations-dictionary}{%
\subsection{Moral Foundations
Dictionary}\label{moral-foundations-dictionary}}

@@

\hypertarget{valence}{%
\subsection{Valence}\label{valence}}

@@

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:exp1-table}stuff at the top}
\begin{tabular}{lccccccc}
\toprule
Foundation & $M_C$ & $SD_C$ & $M_L$ & $SD_L$ & $t$ & $p$ & $d$\\
\midrule
Harm/Care & 0.50 & 2.21 & 0.49 & 2.21 & -0.21 & .850 & 0.01\\
Fairness/Reciprocity & 1.13 & 1.38 & 1.11 & 1.38 & -0.42 & .715 & 0.02\\
Ingroup/Loyalty & 1.28 & 1.63 & 1.34 & 1.63 & 0.30 & .789 & -0.04\\
Authority/Respect & 0.72 & 1.62 & 1.06 & 1.62 & 3.17 & .087 & -0.20\\
Purity/Sanctity & 1.11 & 1.48 & 1.27 & 1.48 & 2.37 & .141 & -0.09\\
\bottomrule
\addlinespace
\end{tabular}
\begin{tablenotes}[para]
\normalsize{\textit{Note.} something useful here}
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

@@

\hypertarget{kavanaugh-supreme-court-hearing}{%
\subsection{Kavanaugh Supreme Court
Hearing}\label{kavanaugh-supreme-court-hearing}}
